### 2018-08-10 CS761-RandomizedAlgorithms/assignments/final.tex
partial 7

>>>>

Choose $c = \min \{\frac{1}{5}, \}$.Let $U = \{u_1,\dots, u_n\}$ be a set of ground elements, and let $S_1, \dots, S_m \subseteq U$ be a set of subsets of $U$ such that $|S_i| = \frac{n}{2}$ for all $i\in [m]$. Consider a uniform random coloring of the elements of $U$ either red or blue. For each $i \in [n]$ let $R_i$ be an indicator random variable for the event that $u_i$ is colored red, and similarly let $B_i$ be an indicator random variable for the event that $u_i$ is colored blue. For each $j \in [m]$ let $R^j := \sum_{u_i \in S_j} R_i$, and similarly let $B^j := \sum_{u_i \in S_j} B_i$. Note that $B^j = |S_j| - R^j$.
First we observe that $R^j$ is the sum of independent random variables with $E[R^j] = \sum_{u_i \in S_j} \frac{1}{2} = \frac{n}{4}$. Further observe that
 $$m \leq {n \choose n/2} \leq 2^{nH(1/2)} = 2^n$$
using that each $S_j$ is of size $\frac{n}{2}$ and the Lemma from Page $1$ of Lecture $12$.  Hence 
$$\frac{4c\sqrt{n\log m}}{n} \leq \frac{4c\sqrt{n^2}}{n}  = 4c < 1.$$
 So by Chernoff,
\begin{align*}
Pr(R^j \geq \frac{n}{4} + c\sqrt{n\log m}) &= Pr(R^j \geq (1+\frac{4c\sqrt{n\log m}}{n})\frac{n}{4})\\
 &\leq e^{-(\frac{4c\sqrt{n\log m}}{n})^2\frac{n}{12}} \\
 &= e^{-\frac{4c^2}{3}\log m}\\
 &=\frac{1}{m^{\frac{4c^2}{3}}}\\
 &!< \frac{1}{m}.
 \end{align*}
